\documentclass[11pt]{article}
\usepackage{graphicx}
\textwidth 15cm
\textheight 22cm
\parindent 10pt
\oddsidemargin 0.85cm
\evensidemargin 0.37cm
\begin{document}
\thispagestyle{empty}
\begin{center}
Vrije Universiteit Amsterdam
\vspace{1mm}

\vspace{1.5cm}
{\Large Bachelor Thesis}
\vspace*{1.5cm}
\rule{.9\linewidth}{.6pt}\\[0.4cm]
{\huge \bfseries Title of the Thesis\par}
{\huge \bfseries Comes Here\par}\vspace{0.4cm}
\rule{.9\linewidth}{.6pt}\\[1.5cm]
\vspace*{2mm}
{\Large
\begin{tabular}{l}
{\bf Author:} ~~Ahmed Driouech ~~~~ (2743820)
\end{tabular}
}
\vspace*{1.5cm}
\begin{tabular}{ll}
{\it 1st supervisor:} & ~~Wan Fokkink \\
{\it 2nd reader:} & ~~supervisor name \\
\end{tabular}
\vspace*{2cm}
\textit{A thesis submitted in fulfillment of the requirements for\\ the VU Bachelor
of Science degree in Computer Science }
\vspace*{1cm}
\today\\[4cm] % Date
\end{center}
\newpage
\textit{A Dutch citizen of age has the right to vote in elections according to article 4 of the constitution[]. Voting is the cornerstone of democracy. It is the means through which the general public can express their opinions and influence the governing of a country. A fair and accurate voting system ensures that the voices of the people are heard and that decisions are made in the best interest of the population. On polling day, all Dutch citizens of age (18 years and older) can cast their vote for a candidate on the candidates list. By casting their vote people chose which party they want to obtain seats in Parliament and perhaps also in the cabinet. At least 14 days before polling day, each eligible person receives a voter registration card and a list of candidates. On polling day, people can cast their votes in person at their local polling station between 7.30 am and 9 pm . For years the process was done with voting machines, however lack of security provisions have resulted in a return to the ballot paper and the red pencil. A three-person committee at the polling station ensures that everything is done according to the rules. The committee collects the polling cards and shows the electors the way to the voting machine or gives them the ballot paper. After the polling stations close at 9 pm the votes are counted. The Central Electoral Office in The Hague then collects all the local polling results, adds them up and determines the overall result of the election[.. , ..].  }
\end{document}
